A community-maintained standard library of population genetic models

### 2020-05-14 response-to-reviewers.md

Dear Graham and the Editorial Board of *eLife*,

Please find attached our revised manuscript entitled, 
"A community maintained standard library of population genetic models"
for consideration for publication.

We thank you and the reviewers of our manuscript for your enthusiasm for our project
and the constructive criticisms that you have raised. As you will find below, we have tried
our level-best to incorporate all of the changes suggested in the reviews. 
While that is so, in a few places we have decided that suggested changes were beyond
the scope of the current manuscript and leave them for future work.

An additional change that has occurred since the first submission of the manuscript
is that the Gutenkunst 2009 model hadn't been through QC, and had a bug.
This has been corrected, resulting in mostly cosmetic changes to the figures and text
(inferred population histories are slightly better than before; see Figure 4);
but we have also explained the situation,
as an example of the utility of QC and the resource more generally.

@@

## Major comments

> 1. Emphasize parameters are current best-guesses:
> a. I am most worried about the fragility of the models over time and the misperception one might have that these models are "accurate" for a species. Genome assemblies change, recombination rates improve, mutation rates change, etc. I would like to see that uncertainty reflected more in the language used in the paper so that it's clear the catalog is a collection of inferred parameters that are subject to change over time. This is a subtle and cosmetic, but important I think. For example, page 4 "the library defines basic information about each species genome, including information about chromosome lengths, average mutation rates, and generation times." Yet, this is information we don't have - each of these parameters is actively under revision/discussion for even the best studied species. It would be great to hammer home these are all inferred values. (Also see page 3 sentence on "details on =the= physical organization of the genome"; the same comment applies, and an improvement might be something like "details on the physical organization of the latest reference genome assembled for the species").

We thank the reviewer for bringing up this important point
and fully agree that the language in the manuscript needs to better emphasize the uncertainty in our current parameter estimates.
To address this, we have made several changes throughout the manuscript, including the passages cited above:

The first quoted passage now reads:
"For each species, the catalog contains curated information on our current understanding of
the physical organization of its genome, inferred genetic maps,
population-level parameters (e.g., mutation rate and generation time estimates),
and published demographic models.
These models and parameters are meant to represent the field's current understanding,
and we intend for this resource to evolve as new results become available, and
other existing models are added to stdpopsim by the community."

The second passage now reads:
"Firstly, the library defines some basic information about our current understanding of each
species' genome, including information about chromosome
lengths, average mutation rate estimates, and generation times.
We also provide access to detailed empirical information such as inferred genetic maps,
which model observed heterogeneity in recombination rate along chromosomes."

@@

> b. On a related note, there is wording on page 4, regarding ensuring "implemented models are accurate" - I think what is meant is that the "implemented models are faithful to the source publications from which they derive". As the second half of this paper makes clear, because of errors in inference, many of these models will not be accurate, in the sense of representing the true history of the species.

We made the suggested change:
"Importantly, we developed rigorous quality control methods to ensure that we have
correctly implemented the models as described in their original publication
and provided documented methods for others to contribute new models."

@@

Moreover we believe that the issues feature on Github provides us with the current utility we need along these lines.

> 3. In terms of the maturity of the examples developed for the initial release, I would have liked to see at least one simulation model with a selective sweep, one with background selection, and one with spatial stepping-stone structure. Each of these would be helpful test cases to implement to be sure that the existing catalog framework has the breadth/flexibility necessary to accommodate future use cases. I do not think this is a requirement for publication, but it would add great value to this initial release of the resource.

As mentioned in our response to the editor's comments, we agree that this is an important avenue to pursue in the near future.
However, performing adequate simulations with selection would require
a substantial amount of additional work and would likely distract from the current relatively simple focus
on inference of demographic history.
We definitely intend to include selection (and expand the available generic models) in future work,
as we now discuss in greater detail in the Discussion ("next steps").

> 4. Page 15. The approach of masking "low-recombination" portions of the chromosomes seems like an incomplete/indirect attempt to model the inherent limitations of sequencing to an "accessible" genome.
> a. Shouldn't the approach instead be to drop "low complexity" regions (e.g., as defined by an excessive number of "N"'s in the reference, low mappability scores, or via tools like RepeatMasker?). This part of the pipeline seems open to refinement.

Our initial motivation for masking was to reduce the overrepresentation of marginal trees with little to no recombination from biasing patterns of diversity in such a way that demographic inference methods would be misled. While we agree with the reviewer that different masking approaches might better reflect the masking done on real genomic data, at this time the best way to mask remains an open question, and we feel that a nuanced analysis of masking is outside the scope of this paper. For these reasons, we feel that masking using a simple recombination rate threshold is a reasonable approach.
We note that there is however a substantial correlation between recombination rate and mappability (by any of the measures mentioned above) wherein the notoriously difficult portions of genomes to assemble are generally in regions of low recombination.
 We agree that there may indeed be better ways to mask, which is why we allow users to mask their simulations as they see fit.

@@

> b. Are the "masks" a separate configuration file for the simulations? It seems that it would be preferable for them to be separate from the recombination rate files - right now it reads as if the mask applied is a function of the genetic map file, but this seems too inflexible for users who prefer an alternative approach to masking.

Mask files are not currently a component of `stdpopsim` proper, rather they were implemented separately from running `stdpopsim`, for the sole purpose of comparing demographic inference methods. All of the masks that we have used are available on the `analysis` repository that is associated with this manuscript. Users who download `stdpopsim` will always be simulating raw and unmasked tree sequence files, to which they can apply any variety of masks *post hoc*, if they so choose.
We are currently making plans, however, to incorporate some version of this process into a future
`stdpopsim` release.

@@

> 2. Little detail is given on the system of identifiers/versioning for models, maps, etc.

True, but the details are rather pedantic and we feel not material for the  manuscript.
We provide a link to our extensive documentation where we describe the system in detail.

> 3. In the abstract, it's left vague what the nature of the resource is.
>
> a. The resource is described as an open source project and a catalog, but the fact that it's a web repository that contains a set of configuration files might be helpful to say explicitly.
> b. Also, while I wouldn't normally include url to software in an abstract, in this special case it seems like it could be very helpful to readers who want to jump right to the resource quickly?

Good point - in the revision we've clarified the nature of the resource,
but haven't included the URL since googling "stdpopsim" features the correct page as the top hit.

@@

> 1) The authors mention that SLiM can be used as an alternative backend, which would presumably allow for simulations with selection. Although I don't think an extensive comparison of selection methods is necessary for this paper, it would be ideal if the authors can give some idea of how this would work (example command line, etc). There are also a myriad of methods for detecting/quantifying selection, and these simulations are not consistent either.

As mentioned in our response to the editor's comment, we added a demonstration of the use of SLiM to the results (see "Simulation engines" section and Supplementary Figures S1 and S2).
See also our response to related comments made by Reviewers #1 and #2.

> 2) I like the inclusion of the "zigzag" history, as well as generic piecewise constant models and IM models (page 7). I wonder if these could be included in a separate section (not organism specific) in the documentation and software (and then in Table 1). Right now the zigzag model is under humans in the catalog.

We considered both of these suggestions, and here's why we've left it the way it is.
Most of the columns of the table don't apply to generic models,
so it seems strange to include them there.
The "zigzag" model could definitely be a generic model,
and indeed was initially implemented as such.
However, the reason we settled on the zigzag model is being defined as a human model is that its
effective population size values are taken from (or at least inspired by) values inferred from human genomes: as implemented, it is not as "generic" as it might seem.

> 3) On page 8 the authors set up notation for the number of replicates (R), number of chromosomes (C), and sample size (n), but don't seem to use it afterward (or use it inconsistently). It would be helpful if all the figure captions and main text included this notation (I am guessing the number of replicates is 3 based on the images, but this should be clarified). The authors use N in the Methods (i.e. page 15) to refer to population size (which makes sense), but then also say "In all cases we set the sample size of the focal population to N = 50 chromosomes." For MSMC, the sample size was set to n=2,8 which suggests haploid samples, but the "Calculating coalescence rates" section says that n is the diploid sample size.

@@

> -Page 6: "time or writing" -> of

Whoops: we corrected this typo.

> -Page 8: "While there is variation in accuracy among methods, populations, and individual replicates, the methods are generally accurate for this model of human history." I'm not sure I agree here (although perhaps relative to other models this statement is true). Discuss a bit more.

"Accurately" is subjective -- we're sure the reviewer can imagine much worse inferences! --
but in any case we've rephrased this bit to say
"While there is variation in accuracy among methods, populations, and individual replicates,
the methods generally produce a good estimate of the true effective population sizes of the
simulations, with inferred values mostly within a factor of two of the truth, and most
methods inferring a bottleneck at approximately the correct time."

@@

> -Page 12: S7, S4, S6 are mentioned in a different order than they appear in the supplement (I understand why but maybe revisit this part)

We reordered the figures to make sure they were referenced in the same order they appear in the supplement.

> -Page 13: "overfit the YRI history" do you mean overfit in a technical sense?

We meant to say that the inferred history has more population size changes than the truth did;
but this phrase has been removed.

### 2020-05-14 response-to-reviewers.md

> 1) The authors mention that SLiM can be used as an alternative backend, which would presumably allow for simulations with selection. Although I don't think an extensive comparison of selection methods is necessary for this paper, it would be ideal if the authors can give some idea of how this would work (example command line, etc). There are also a myriad of methods for detecting/quantifying selection, and these simulations are not consistent either.

As mentioned in our response to the editor's comment, we added a demonstration of the use of SLiM to the results (see "Simulation engines" section and Supplementary Figures S1 and S2).
See also our response to related comments made by Reviewers #1 and #2.

> 2) I like the inclusion of the "zigzag" history, as well as generic piecewise constant models and IM models (page 7). I wonder if these could be included in a separate section (not organism specific) in the documentation and software (and then in Table 1). Right now the zigzag model is under humans in the catalog.

We considered both of these suggestions, and here's why we've left it the way it is.
Most of the columns of the table don't apply to generic models,
so it seems strange to include them there.
The "zigzag" model could definitely be a generic model,
and indeed was initially implemented as such.
However, the reason we settled on the zigzag model is being defined as a human model 
(see discussion at https://github.com/popsim-consortium/stdpopsim/issues/106)
is that its effective population size values are taken from (or at least inspired by) values inferred from human genomes: as implemented, it is not as "generic" as it might seem.

### 2020-05-15 response-to-reviewers.md

We fully agree that the language in the original manuscript was not careful enough in conveying uncertainty about the models and parameters we discuss.
We have made edited the text throughout the manuscript to address this.
See our response to Reviewer 1 below for examples.
We have also added a bit more to the discussion (below "next steps") on this point.

> 2) We would like to see the SLIM integration demonstrated with an application that msprime doesn't cover. This could be, for example, a figure of the average value some summary statistics surrounding a selective under the human demographic model. The reviewers didn't want this to be a lot of work, e.g., it would be outside of the scope of the current paper to demonstrate the power of a range of selection methods. However, we felt that a simple demonstration of the functionality would substantially increase the scenarios easily available and imaginable by readers of the paper.

We would like to see this also and agree that it would be of great interest.
However, we felt that performing adequate simulations with selection would require
a substantial amount of additional work and would significantly expand the scope of
the manuscript.
Furthermore, discussing selection would distract from the current relatively simple focus
on inference of demographic history.
We definitely intend to include selection (and expand the available generic models) in future work,
as we now discuss in greater detail in the Discussion ("next steps").

Instead, we have decided to add a section validating the use of SLiM in stdpopsim neutral simulations (see "simulation engines" section in the results and Supplementary Figures S1 and S2).
Our focus there was to show that under neutral simulations, SLiM produced data that were consistent with the coalescent simulations of msprime.
To expand on this fundamental point, we also examined the influence of population size down-scaling, which is a common practice used in forward simulations, and indeed often crucial for tractable compute times.
While this is by no means a comprehensive investigation into this issue, we do believe that it demonstrates the use of SLiM in future applications that will also simulate selection.

@@

> 6. Page 6. Typo in "time or writing". Change to "time of writing"

Thanks for spotting this typo! We corrected it.

> 7. Page 8. I like the approach of showing inverse coalescent rates, but it would be instructive to practitioners and useful for teaching, if in all figures you showed both the census sizes (e.g. with light grey dashed lines) and inverse rates (e.g. with dark grey solid lines as now in Fig 2).

First, we note that we decided to avoid using "census size", and simply refer to it as the "simulated population size", as we realized the use of "census" here could be misleading (see below for further discussion). Regarding the main point raised by the reviewer, we agree that in the single-population analyses, it would be instructive to show both the simulated (census) population size and the inverse coalescence rates. We thus plotted the simulated population sizes against the inverse coalescence rate for the model used in Figure 2, and found that they were near identical. As a result, we decided to show this comparison in Supplementary Figure S3 and discuss this issue in the text without adding the simulated population sizes to the main figures (as they didn't appear to add much). Note that in the multi-population analyses, the inverse coalescence rate is less appropriate, because some of the inference methods used in these analyses model gene flow, and should therefore be able to recover the true simulated population sizes. We now clarify this in the text as well.

### 2020-05-15 popSimManu.tex
cleaned up single data is instance
closes #203

%ACS: the consortium really isn't the point; let's get right to describing what stdpopsim is
%The first contribution of the PopSim consortium is
The \stdpopsim library is
a community-maintained collection of empirical genome data and population genetics simulation models,
illustrated in Figure \ref{fig:cartoon}.
The package centers on a catalog of genomic information and demographic models
for a growing list of species (Fig.~\ref{fig:cartoon}A),
and software resources to facilitate efficient simulations (Fig.~\ref{fig:cartoon}B-C).

Given the genome data and simulation model descriptions defined within the
library, it is straightforward to run standardized simulations
across a range of organisms. \Stdpopsim has a Python API and a user-friendly
command line interface, allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the ``succinct tree sequence''
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed efficiently using the \tskit library
\citep{kelleher2016efficient,kelleher2018efficient}.
The tree sequence format could also be converted
to other formats (e.g., VCF) by the user if desired.

@@

The central feature of \stdpopsim is the species catalog, a systematic organization
of the key quantitative data needed to simulate a given species.
Data is currently available for humans,
\textit{P.~abelii}, \textit{C.~familiaris},
\textit{D.~melanogaster}, \textit{A.~thaliana},
and \textit{E.~coli}.
A species definition consists of two key elements.
Firstly, the library defines some basic information about our current understanding of each
species' genome, including information about chromosome
lengths, average mutation rate estimates, and generation times.
We also provide access to detailed empirical information such as inferred genetic maps,
which model observed heterogeneity in recombination rate along chromosomes.
Such maps are often large,
so we do not distribute them directly with the software, but make them available
for download in a standard format.
When a simulation using such a map is requested by the user,
\stdpopsim will transparently download the map data into a local cache,
% (\texttt{$\sim$/.local/cache/stdpopsim} by default on Unix platforms)
where it can be quickly retrieved for subsequent simulations.
In the initial version of \stdpopsim we support
the HapMapII~\citep{international2007second} and
deCODE~\citep{kong2010fine} genetic maps for humans;
the \cite{nater2017morphometric} maps for \textit{P.~abelii};
the \cite{campbell2016pedigree} map for \textit{C.~familiaris};
the \cite{salome2011recombination} map for \textit{A.~thaliana};
and the \cite{comeron2012many} map for \textit{D.~melanogaster}. 
Adding further maps to the library is straightforward.
The second key element of a species description
within \stdpopsim is a set of carefully curated population genetic model
descriptions from the literature, which allow simulation under
specific historical scenarios that have been fit to present-day patterns of
genetic variation (See the Methods for a description of the community
development and quality-control process for these models.)
\renewcommand{\arraystretch}{1.2}
\begin{table}[t]
% Make sure the table is centered even though it's too wide
\makebox[\textwidth][c]{
    \begin{footnotesize}
    \input{model_table.tex}
    \end{footnotesize}
}
\caption{\label{tab:catalog}
Initial set of demographic models in the catalog and summary of computing resources needed for simulation.
For each model, we report the CPU time, maximum memory usage and the
size of the output \tskit file, as simulated using the \texttt{msprime}
simulation engine (version 0.7.4).
In each case, we simulate 100 samples
drawn from the first population, for the shortest chromosome of that species
and a constant chromosome-specific recombination rate.
The times reported are for a single run on an Intel i5-7600K CPU.
Computing resources required will vary widely depending on sample sizes, chromosome length,
recombination rates and other factors.
}
\end{table}

@@

%DRS: do we want to include these generic models in Table 1?
%ADK: not a bad idea...

@@

\paragraph{Benchmarking population size inference.}
We have illustrated in this paper how \stdpopsim can be used for direct
comparisons of inferential methods on a common set of simulations. Our
benchmarking comparisons have been limited, but nevertheless
reveal some informative features.
For example, at the task of estimating population size histories for simulated human
populations, we find that the sequence-based methods (\MSMC and \smcpp)
perform somewhat better overall---at least for moderate times in the past---than
the site frequency spectrum-based method (\stairwayplot),
which tends to over-estimate the sizes of oscillations
(Figures~\ref{fig:n_t_ragsdale} and~\ref{fig:n_t_gutenkunst}).
In contrast, \stairwayplot outperforms the sequence-based methods
on simulations of \textit{D.~melanogaster} or \textit{A.~thaliana} populations,
in which linkage disequilibrium is reduced (Figures~\ref{fig:n_t_sheehan} \& \ref{fig:n_t_AraTha}).
In simulations of two human populations
(Figure~\ref{fig:IM_popn_human}), \dadi and \fastsimcoal do reasonably well at
reconstructing the simulated YRI history and estimating divergence times, but struggle with the more complex simulated CEU
history, in large part because the methods assume constant population sizes.
On the other hand, \smcpp does not have the same
restrictions on its inferred history, and as a result does much better
with the CEU history but tends to underestimate divergence times
due to the assumption of no migration.
The results for the two-population \textit{D.~melanogaster} model (Figure~\ref{fig:two_popn_fly}) are generally similar.
In these comparisons, \fastsimcoal and \dadi perform almost identically, which is expected because they fit the same models to the same summaries of the data,
differing only in how they calculate model expectations and optimize parameters.

@@

% note: this is addressing reviewer comments about model uncertainty
We wish to emphasize that although the included demographic histories are some of the
most widely used models for our current set of species,
we anticipate the set of available models to expand
as new methods and new modeling frameworks are developed.
For instance, the current models all describe a small set of discrete, randomly mating populations,
which are likely good approximations for deep-time population history,
but may be less useful for methods describing dynamics of contemporary populations.
\Stdpopsim's framework is sufficiently general that more realistic population models
will be easily incorporated, as they are published.

%ADK: I cut this off here-- I think thais is a fine ending

%Our current set of models is not exhaustive at this point however,
%and othercan be readily incorporated into \stdpopsim.
%Additional complications such as changing
%genome builds as assemblies improve must also be incorporated.
%As the collection of models and species grows, we hope to
%incorporate crowd-sourced community input
%to highlight the most appropriate models and genome annotations.
%DRS: not in love with the word "annotations" here as some might think we are talking gene annotations (which we will be eventually but not yet), but "details" is too vague.

>>>>

%ACS: the consortium really isn't the point; let's get right to describing what stdpopsim is
%The first contribution of the PopSim consortium is
The \stdpopsim library is
a community-maintained collection of empirical genome data and population genetics simulation models,
illustrated in Figure \ref{fig:cartoon}.
The package centers on a catalog of genomic information and demographic models
for a growing list of species (Fig.~\ref{fig:cartoon}A),
and software resources to facilitate efficient simulations (Fig.~\ref{fig:cartoon}B-C).
Given the genome data and simulation model descriptions defined within the
library, it is straightforward to run standardized simulations
across a range of organisms. \Stdpopsim has a Python API and a user-friendly
command line interface, allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the ``succinct tree sequence''
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed efficiently using the \tskit library
\citep{kelleher2016efficient,kelleher2018efficient}.
The tree sequence format could also be converted
to other formats (e.g., VCF) by the user if desired.

@@

The central feature of \stdpopsim is the species catalog, a systematic organization
of the key quantitative data needed to simulate a given species.
Data are currently available for humans,
\textit{P.~abelii}, \textit{C.~familiaris},
\textit{D.~melanogaster}, \textit{A.~thaliana},
and \textit{E.~coli}.
A species definition consists of two key elements.
Firstly, the library defines some basic information about our current understanding of each
species' genome, including information about chromosome
lengths, average mutation rate estimates, and generation times.
We also provide access to detailed empirical information such as inferred genetic maps,
which model observed heterogeneity in recombination rate along chromosomes.
Such maps are often large,
so we do not distribute them directly with the software, but make them available
for download in a standard format.
When a simulation using such a map is requested by the user,
\stdpopsim will transparently download the map data into a local cache,
% (\texttt{$\sim$/.local/cache/stdpopsim} by default on Unix platforms)
where it can be quickly retrieved for subsequent simulations.
In the initial version of \stdpopsim we support
the HapMapII~\citep{international2007second} and
deCODE~\citep{kong2010fine} genetic maps for humans;
the \cite{nater2017morphometric} maps for \textit{P.~abelii};
the \cite{campbell2016pedigree} map for \textit{C.~familiaris};
the \cite{salome2011recombination} map for \textit{A.~thaliana};
and the \cite{comeron2012many} map for \textit{D.~melanogaster}. 
Adding further maps to the library is straightforward.
The second key element of a species description
within \stdpopsim is a set of carefully curated population genetic model
descriptions from the literature, which allow simulation under
specific historical scenarios that have been fit to present-day patterns of
genetic variation (See the Methods for a description of the community
development and quality-control process for these models.)
\renewcommand{\arraystretch}{1.2}
\begin{table}[t]
% Make sure the table is centered even though it's too wide
\makebox[\textwidth][c]{
    \begin{footnotesize}
    \input{model_table.tex}
    \end{footnotesize}
}
\caption{\label{tab:catalog}
Initial set of demographic models in the catalog and summary of computing resources needed for simulation.
For each model, we report the CPU time, maximum memory usage and the
size of the output \tskit file, as simulated using the \texttt{msprime}
simulation engine (version 0.7.4).
In each case, we simulate 100 samples
drawn from the first population, for the shortest chromosome of that species
and a constant chromosome-specific recombination rate.
The times reported are for a single run on an Intel i5-7600K CPU.
Computing resources required will vary widely depending on sample sizes, chromosome length,
recombination rates and other factors.
}
\end{table}

@@

@@

\paragraph{Benchmarking population size inference.}
We have illustrated in this paper how \stdpopsim can be used for direct
comparisons of inferential methods on a common set of simulations. Our
benchmarking comparisons have been limited, but nevertheless
reveal some informative features.
For example, at the task of estimating population size histories for simulated human
populations, we find that the sequence-based methods (\MSMC and \smcpp)
perform somewhat better overall---at least for moderate times in the past---than
the site frequency spectrum-based method (\stairwayplot),
which tends to over-estimate the sizes of oscillations
(Figures~\ref{fig:n_t_ragsdale} and~\ref{fig:n_t_gutenkunst}).
In contrast, \stairwayplot outperforms the sequence-based methods
on simulations of \textit{D.~melanogaster} or \textit{A.~thaliana} populations,
in which linkage disequilibrium is reduced (Figures~\ref{fig:n_t_sheehan} and \ref{fig:n_t_AraTha}).
In simulations of two human populations
(Figure~\ref{fig:IM_popn_human}), \dadi and \fastsimcoal do reasonably well at
reconstructing the simulated YRI history and estimating divergence times, but struggle with the more complex simulated CEU
history, in large part because the methods assume constant population sizes.
On the other hand, \smcpp does not have the same
restrictions on its inferred history, and as a result does much better
with the CEU history but tends to underestimate divergence times
due to the assumption of no migration.
The results for the two-population \textit{D.~melanogaster} model (Figure~\ref{fig:two_popn_fly}) are generally similar.
In these comparisons, \fastsimcoal and \dadi perform almost identically, which is expected because they fit the same models to the same summaries of the data,
differing only in how they calculate model expectations and optimize parameters.

@@

% note: this is addressing reviewer comments about model uncertainty
We wish to emphasize that although the included demographic histories are some of the
most widely used models for our current set of species,
we anticipate the set of available models to expand
as new methods and new modeling frameworks are developed.
For instance, the current models all describe a small set of discrete, randomly mating populations,
which are likely good approximations for deep-time population history,
but may be less useful for methods describing dynamics of contemporary populations.
\Stdpopsim's framework is sufficiently general that more realistic population models
will be easily incorporated, as they are published.
Additional aspects of the framework,
such as genome builds, will also continue to change
as improvements are made to our understanding of genome structure.

%As the collection of models and species grows, we hope to
%incorporate crowd-sourced community input
%to highlight the most appropriate models and genome annotations.
%DRS: not in love with the word "annotations" here as some might think we are talking gene annotations (which we will be eventually but not yet), but "details" is too vague.
